Shaping Anti-Corruption Campaigns in Nigeria

### 2024-12-04 paper/paper.qmd
final edits!!

The remainder of this paper is structured as follows; @sec-data details the data used for this paper, @sec-model introduces the Bayesian ordinal logistic regression model used to study the relationship between our variables of interest. @sec-results presents the findings from the model, detailing how different demographic factors like education and age affect corruption perception in Nigeria. @sec-discussion examines these results, discussing their implications for anti-corruption policies, weaknesses and next steps. @sec-survey-appendix explores the details of the Afrobarometer survey. @sec-model-details shows plots for Posterior predictive checks and Diagnostics as well as their analysis. @sec-survey-appendix details the survey methodology used in the Afrobarometer data and @sec-ethics addresses very important ethical principles and the ethical challenges of surveying sensitive topics like corruption.@sec-Data-Driven-Narrative-appendix introduces a narrative example, 'Amina's Story,' to humanize the data by showing how demographic factors like age, education, and urban residency shape individual perceptions of corruption, while emphasizing the ethical importance of considering the lived experiences behind the data.

@@

# Amina's Story - A Personal Perspective {#sec-Data-Driven-Narrative-appendix}

>>>>

The remainder of this paper is structured as follows; @sec-data details the data used for this paper, @sec-model introduces the Bayesian ordinal logistic regression model used to study the relationship between our variables of interest. @sec-results presents the findings from the model, detailing how different demographic factors like education and age affect corruption perception in Nigeria. @sec-discussion examines these results, discussing their implications for anti-corruption policies, weaknesses and next steps. @sec-survey-appendix explores the details of the Afrobarometer survey. @sec-model-details shows plots for Posterior predictive checks and Diagnostics as well as their analysis. @sec-survey-appendix details the survey methodology used in the Afrobarometer data and @sec-ethics addresses very important ethical principles and the ethical challenges of surveying sensitive topics like corruption. @sec-narrative introduces a narrative example, 'Amina's Story,' to humanize the data by showing how demographic factors like age, education, and urban residency shape individual perceptions of corruption, while emphasizing the ethical importance of considering the lived experiences behind the data.

@@

# Amina's Story - A Personal Perspective {#sec-narrative}
